Using best practices for forecasting biodiversity changes in breeding birds

### 2017-07-28 manuscript/draft.Rmd
Remove reference to "sites" at first mention of SDMs
Since lots of these are built using grid cells it's not quite right and I think it actually reads fine just by removing the specifics.
Fix `(Box 1)` related rendering
typo

Previous efforts to predict future patterns of species richness, and diversity
more generally, have focused primarily on building species distributions models.
In general, these models describe individual species' occurrence patterns across
sites as functions of the site's environment [@thomas2004; @urban2015]. By
plugging forecasts of future environmental conditions into these functions,
ecologists can make predictions about where each species will occur in the
future. These species-level predictions can then be added up ("stacked") to
generate predicted richness values [e.g. @calabrese2014]. Alternatively, models
that directly relate spatial patterns of species richness to the environment
have been developed and generally perform equivalently to species distribution
modeling based methods [@algar2009; @distler2015]. This approach is sometimes
referred to as "macroecological" modeling, because it models the larger-scale
pattern (richness) more directly [@distler2015].

@@

The most commonly used method to forecast future biodiversity, stacked SDMS
[@urban2015], provided the worst overall forecasts of all methods evaluated. In
general, SDM-based forecasts are rarely evaluated, particularly in terms of
repeated observations at the same site. Since site-level richness is relatively
stable, model evaluations that show high accuracy in predicting differences
among sites may not indicate much about a model's ability to predict changes
over time. This issue has also recently been recently highlighted as an issue
for using SDMs to predict the future locations of individual species
[@rapacciuolo2012]. This result is particularly sobering because this approach
forms the main foundation for estimates of the predicted loss of biodiversity to
climate change [@thomas2004; @urban2015]. The poor performance of SDM-based
forecasts highlights the crucial importance of comparing multiple modeling
approaches when conducting ecological forecasts, and in particular the value of
comparing results to simple baselines to avoid over-interpreting the information
present in these forecasts (Box 1).  Disciplines that have more mature forecasting
cultures often do this by reporting "forecast skill", which is the improvement
in the forecast relative to a simple baseline [@jolliffe2003]. We recommend
following Ye et al. [@ye2015] and adopting this approach in future ecological
forecasting research. It also highlights the need for using hindcasting and
time-series data for assessing the effectiveness of forecasting methods, since
this allows comparisons to baselines and assessment of predicted dynamics within
sites or regions.

>>>>

Previous efforts to predict future patterns of species richness, and diversity
more generally, have focused primarily on building species distributions models.
In general, these models describe individual species' occurrence patterns as
functions of the environment [@thomas2004; @urban2015]. By plugging forecasts of
future environmental conditions into these functions, ecologists can make
predictions about where each species will occur in the future. These
species-level predictions can then be added up ("stacked") to generate predicted
richness values [e.g. @calabrese2014]. Alternatively, models that directly
relate spatial patterns of species richness to the environment have been
developed and generally perform equivalently to species distribution modeling
based methods [@algar2009; @distler2015]. This approach is sometimes referred to
as "macroecological" modeling, because it models the larger-scale pattern
(richness) more directly [@distler2015].

@@

The most commonly used method to forecast future biodiversity, stacked SDMS
[@urban2015], provided the worst overall forecasts of all methods evaluated. In
general, SDM-based forecasts are rarely evaluated, particularly in terms of
repeated observations at the same site. Since site-level richness is relatively
stable, model evaluations that show high accuracy in predicting differences
among sites may not indicate much about a model's ability to predict changes
over time. This issue has also recently been highlighted as an issue
for using SDMs to predict the future locations of individual species
[@rapacciuolo2012]. This result is particularly sobering because this approach
forms the main foundation for estimates of the predicted loss of biodiversity to
climate change [@thomas2004; @urban2015]. The poor performance of SDM-based
forecasts highlights the crucial importance of comparing multiple modeling
approaches when conducting ecological forecasts, and in particular the value of
comparing results to simple baselines to avoid over-interpreting the information
present in these forecasts (Box 1).  Disciplines that have more mature forecasting
cultures often do this by reporting "forecast skill", which is the improvement
in the forecast relative to a simple baseline [@jolliffe2003]. We recommend
following Ye et al. [@ye2015] and adopting this approach in future ecological
forecasting research. It also highlights the need for using hindcasting and
time-series data for assessing the effectiveness of forecasting methods, since
this allows comparisons to baselines and assessment of predicted dynamics within
sites or regions.
